---
title: "Community detection"
description: |
  An attempt at community detection on the dyadic conflict dataset. Discussions on issues faced and alternate strategies. Also contains the full network visualization.
author:
  - name: Abhijit Mahishi
    url: {https://abhijit156.github.io/}
date: 2022-05-12
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(igraph)
library(stringr)
library(tidyverse)
library(network)
library(ggplot2)
library(visNetwork)
library(corrr)
library(sna)
library(asnipe)

```

```{r}

knitr::opts_chunk$set(echo = FALSE)

conflict <- read.csv("/Users/abhijit/Desktop/Spring22/Networks/Data/ucdp-dyadic-211.csv", header=TRUE)

conflict_subset <- conflict #%>% filter((type_of_conflict == 3) & (region == 3))

conflict_subset <- conflict_subset[,c(4,7,10,11,12,13,14,15,16,17,18,24,1,2,3)]
conflict_subset$region <- as.integer(conflict_subset$region)
conflict_subset$disp_region <- ifelse(conflict_subset$region == 1, "Europe",
                                      ifelse(conflict_subset$region == 2, "Middle East",
                                             ifelse(conflict_subset$region == 3, "Asia",
                                                    ifelse(conflict_subset$region == 4, "Africa","Americas" ))))
conflict_subset$side_a <- gsub("Government of ","",as.character(conflict_subset$side_a))


graph <- graph.data.frame(conflict_subset)

net<- as.network(conflict_subset, matrix.type = "edgelist", multiple = T)

vn <- toVisNetworkData(graph)
```

# Attempting to create community clusters by converting network into undirected graph

```{r}
knitr::opts_chunk$set(echo = TRUE)
#comm.fg<-cluster_fast_greedy(as.undirected(graph))
#comm.fg
#igraph::groups(comm.fg)
```

```{r}
knitr::opts_chunk$set(echo = FALSE)
country_labels = unique(conflict_subset$side_a)

vn$nodes$color <- ifelse(vn$nodes$id %in% country_labels, "green","tomato")
vn$nodes$group <- conflict$disp_region

vn$edges$title <- paste(vn$edges$territory_name, vn$edges$year, sep = " - ")
vn$edges$color <- ifelse(vn$edges$incompatibility == 1, "lightcyan4",ifelse(vn$edges$incompatibility == 2,"orange","blue"))

```

# Instead of communities, trying to plot the network with defined groups for each Region

Since the network created by the dyadic conflict dataset is directed and has multiple edges between nodes, after trying multiple methods from different packages, it seems like community detection will not be possible on this network. This is an important consideration to make and explore in further studies.

```{r}
knitr::opts_chunk$set(echo = TRUE)
visNetwork(nodes = vn$nodes, edges = vn$edges, height = "1000px", width = "2400px") %>%
  visOptions(highlightNearest = TRUE) %>% 
  visLegend(enabled = TRUE,position = 'right') %>%
  visGroups(groupname = "Europe", color = "red", shape = "database") %>%
  visGroups(groupname = "Middle East", color = "yellow", shape = "triangle") %>%
  visGroups(groupname = "Asia", color = "green", shape = "circle") %>%
  visGroups(groupname = "Africa", color = "brown", shape = "square") %>%
  visGroups(groupname = "Americas", color = "blue", shape = "dot") %>%
  visInteraction(multiselect = TRUE, navigationButtons=TRUE,dragNodes=TRUE,dragView=TRUE,zoomView=TRUE, hideEdgesOnZoom = TRUE, hideEdgesOnDrag = TRUE,hoverConnectedEdges = TRUE) %>%
  visEdges(label = vn$edges$title, physics = TRUE,labelHighlightBold = TRUE, color = vn$edges$color) %>%
  visNodes(shape = 'dot', label = vn$nodes$label, title = vn$nodes$id, labelHighlightBold = TRUE, borderWidth = 1.25, borderWidthSelected = 1.75) %>%
  visExport(type = "png", name = "export-network", 
   float = "left", background = "purple", style= "") 

 
```
