---
title: "Network Status"
description: |
  Exploring network status of armed conflict dataset
author:
  - name: Abhijit Mahishi
    url: {https://abhijit156.github.io/}
date: 2022-05-11
output:
  distill::distill_article:
    self_contained: false
draft: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r}
knitr::opts_chunk$set(echo = FALSE)

library(igraph)
library(stringr)
library(tidyverse)
library(network)
library(ggplot2)
library(visNetwork)
library(corrr)

```

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.
```{r}
knitr::opts_chunk$set(echo = FALSE)

conflict <- read.csv("/Users/abhijit/Desktop/Spring22/Networks/Data/ucdp-dyadic-211.csv", header=TRUE)

conflict_subset <- conflict %>% filter((type_of_conflict == 3) & (region == 3))

conflict_subset <- conflict_subset[,c(4,7,10,11,12,13,14,15,16,17,18,1,2,3)]

graph <- graph.data.frame(conflict_subset)
```

# Calculating Eigen centrality and Bonacich Power centrality

```{r}
graph.nodes<-data.frame(name=V(graph)$name,
degree=igraph::degree(graph))

graph.nodes<-graph.nodes %>%
mutate(indegree=igraph::degree(graph, mode="in",loops=FALSE),
outdegree=igraph::degree(graph, mode="out",loops=FALSE))

temp<-igraph::centr_eigen(graph,directed=T)
graph.nodes$eigen = temp$vector

head(power_centrality(graph))

graph.nodes$bonpow<-power_centrality(graph)


```
Since the graph is directed and acyclic, the eigenvector values are always 0. Thus, calculating node-level Bonacich Power centrality. As expected, the Bonacich power centrality of countries like Myanmar, India, Philippines with high outdegree is the highest.

Derived 
```{r}
mat<-as.matrix(as_adjacency_matrix(graph))
matsq <- t(mat) %*% mat
graph.nodes$rc<-diag(matsq)/rowSums(matsq)
graph.nodes$rc<-ifelse(is.nan(graph.nodes$rc),0,graph.nodes$rc)
graph.nodes$eigen.rc<-graph.nodes$eigen*graph.nodes$rc

#Calculate the proportion of derived centrality.
graph.nodes$dc<-1-diag(matsq)/rowSums(matsq)
#replace missing values with 0
graph.nodes$dc<-ifelse(is.nan(graph.nodes$dc),1,graph.nodes$dc)
#Calculate received eigenvalue centrality
graph.nodes$eigen.dc<-graph.nodes$eigen*graph.nodes$dc
```
Plotting
```{r}
graph.nodes%>%
select(-name) %>%
gather() %>%
ggplot(aes(value)) +
geom_histogram() +
facet_wrap(~key, scales = "free")

## `stat_bin()` using `bins = 30`. Pick better value with `binwidth`.

```
Correlations
```{r}
temp<-graph.nodes %>%
select(degree,indegree,outdegree, starts_with("bon"))%>% correlate() %>% rearrange()
rplot(temp)
```
The plot confirms a high correlation between a node's degree and bonacich power as observed earlier in the analysis.
