---
title: "Structural Equivalence"
description: |
  Exploring network structural equivalence of armed conflict dataset
author:
  - name: Abhijit Mahishi
    url: {https://abhijit156.github.io/}
date: 2022-05-11
output:
  distill::distill_article:
    self_contained: false
draft: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Assignment tasks
-   Measure aspects of network role equivalence

-   Partition network into positions based on clustering results

-   Understanding Blockmodel and plot positions


```{r}
knitr::opts_chunk$set(echo = FALSE)

library(igraph)
library(stringr)
library(tidyverse)
library(network)
library(ggplot2)
library(visNetwork)
library(intergraph)
library(corrr)
library(sna)
```

# Implementing for Asian region
```{r}
knitr::opts_chunk$set(echo = TRUE)

conflict <- read.csv("/Users/abhijit/Desktop/Spring22/Networks/Data/ucdp-dyadic-211.csv", header=TRUE)

conflict_subset <- conflict %>% filter((region == 3))

conflict_subset <- conflict_subset[,c(4,7,10,11,12,13,14,15,16,17,18,1,2,3)]
conflict_subset$side_a <- gsub("Government of ","",as.character(conflict_subset$side_a))

graph <- graph.data.frame(conflict_subset)
```

# Creating matrix to analyze structural equivalence

```{r}
knitr::opts_chunk$set(echo = TRUE)

cs <- as.matrix(conflict_subset)
#create igraph object from data
ig <- graph_from_data_frame(cs, directed = TRUE)
# add edge attribute weight i.e transfer fee
ig <- set_edge_attr(ig, "weight", value = conflict_subset$intensity_level)

#check summary of the igraph object
summary(ig)

net <- intergraph::asNetwork(ig) 
net
```

# Plotting structural equivalence graphs

```{r}
matr<- as.matrix(as_adjacency_matrix(ig, attr = "weight"))
transfer.se<-equiv.clust(matr, equiv.fun="sedist", cluster.method="average", method="hamming",mode="digraph")
plot(transfer.se,labels=transfer.se$glabels)
rect.hclust(transfer.se$cluster, k = 3) 

plot_dendrogram(cluster_leading_eigen(as.undirected(ig)), mode = igraph_opt("dend.plot.type")) 


```

# Block modeling
```{r}
g_mat <- as.matrix(get.adjacency(simplify(ig)))
g_eq <- equiv.clust(g_mat, mode = "graph")
plot(g_eq)

g_block <- blockmodel(g_mat, g_eq, h= 5, mode="graph")
plot(g_block, cex=0.1)

gplot(g_mat, vertex.col = g_block$block.membership, gmode="graph")

gplot(g_block$block.model, gmode="graph", label=rownames(g_block$block.model), edge.lwd = g_block$block.model*10)

plot(density(g_block$block.membership))

```
# Implementing for the African region
```{r}
knitr::opts_chunk$set(echo = TRUE)

conflict <- read.csv("/Users/abhijit/Desktop/Spring22/Networks/Data/ucdp-dyadic-211.csv", header=TRUE)

conflict_subset <- conflict %>% filter((region == 4))

conflict_subset <- conflict_subset[,c(4,7,10,11,12,13,14,15,16,17,18,1,2,3)]
conflict_subset$side_a <- gsub("Government of ","",as.character(conflict_subset$side_a))

graph <- graph.data.frame(conflict_subset)
```

# Creating matrix to analyze structural equivalence

```{r}
knitr::opts_chunk$set(echo = TRUE)

cs <- as.matrix(conflict_subset)
#create igraph object from data
ig <- graph_from_data_frame(cs, directed = TRUE)
# add edge attribute weight i.e transfer fee
ig <- set_edge_attr(ig, "weight", value = conflict_subset$intensity_level)

#check summary of the igraph object
summary(ig)

net <- intergraph::asNetwork(ig) 
net
```

# Plotting structural equivalence graphs

```{r}
matr<- as.matrix(as_adjacency_matrix(ig, attr = "weight"))
transfer.se<-equiv.clust(matr, equiv.fun="sedist", cluster.method="average", method="hamming",mode="digraph")
plot(transfer.se,labels=transfer.se$glabels)
rect.hclust(transfer.se$cluster, k = 3) 

plot_dendrogram(cluster_leading_eigen(as.undirected(ig)), mode = igraph_opt("dend.plot.type")) 


```

# Block modeling
```{r}
g_mat <- as.matrix(get.adjacency(simplify(ig)))
g_eq <- equiv.clust(g_mat, mode = "graph")
plot(g_eq)

g_block <- blockmodel(g_mat, g_eq, h= 5, mode="graph")
plot(g_block, cex=0.1)

gplot(g_mat, vertex.col = g_block$block.membership, gmode="graph")

gplot(g_block$block.model, gmode="graph", label=rownames(g_block$block.model), edge.lwd = g_block$block.model*10)

plot(density(g_block$block.membership))

```

