---
title: "Network Brokerage"
description: |
  Exploring network brokerage of armed conflict dataset
author:
  - name: Abhijit Mahishi
    url: {https://abhijit156.github.io/}
date: 2022-05-11
output:
  distill::distill_article:
    self_contained: false
draft: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
# Assignment tasks
-   Measure aspects of network brokerage

-   Include node level measures like closeness and betweenness centrality

-   Include network level measures like closeness and betweenness centralization and constraint


```{r}
knitr::opts_chunk$set(echo = FALSE)

library(igraph)
library(stringr)
library(tidyverse)
library(network)
library(ggplot2)
library(visNetwork)
library(corrr)
library(sna)

```

```{r}
knitr::opts_chunk$set(echo = FALSE)

conflict <- read.csv("/Users/abhijit/Desktop/Spring22/Networks/Data/ucdp-dyadic-211.csv", header=TRUE)

conflict_subset <- conflict #%>% filter((type_of_conflict == 3) & (region == 3))

conflict_subset <- conflict_subset[,c(4,7,10,11,12,13,14,15,16,17,18,1,2,3)]
conflict_subset$side_a <- gsub("Government of ","",as.character(conflict_subset$side_a))

graph <- graph.data.frame(conflict_subset)
```

# Graph nodes dataset 


Creating a dataframe where all node-level centrality scores and attributes are stored

```{r}
knitr::opts_chunk$set(echo = TRUE)

graph.nodes<-data.frame(name=V(graph)$name,
degree=igraph::degree(graph))

graph.nodes<-graph.nodes %>%
mutate(indegree=igraph::degree(graph, mode="in",loops=FALSE),
outdegree=igraph::degree(graph, mode="out",loops=FALSE))

temp<-igraph::centr_eigen(graph,directed=T)
graph.nodes$eigen = temp$vector

head(power_centrality(graph))

graph.nodes$bonpow<-power_centrality(graph)

mat<-as.matrix(as_adjacency_matrix(graph))
matsq <- t(mat) %*% mat
graph.nodes$rc<-diag(matsq)/rowSums(matsq)
graph.nodes$rc<-ifelse(is.nan(graph.nodes$rc),0,graph.nodes$rc)
graph.nodes$eigen.rc<-graph.nodes$eigen*graph.nodes$rc

#Calculate the proportion of derived centrality.
graph.nodes$dc<-1-diag(matsq)/rowSums(matsq)
#replace missing values with 0
graph.nodes$dc<-ifelse(is.nan(graph.nodes$dc),1,graph.nodes$dc)
#Calculate received eigenvalue centrality
graph.nodes$eigen.dc<-graph.nodes$eigen*graph.nodes$dc

```



# Closeness Centrality 
```{r}
head(igraph::closeness(graph))

centr_clo(graph)$centralization

```
Closeness centrality is the sum of geodesic distances between a node and all other nodes in the network. Since this network is a disconnected graph, the closeness centrality is not well-defined. Similarly, the network centralization is not well-defined due to the graph being disconnected. 

```{r}
#print(igraph::betweenness(graph, directed=TRUE))

centr_betw(graph,directed=T)$centralization

constraint(graph)

graph.nodes$constraint<-constraint(graph)
#find the nodes with highest and lowest constraint
arrange(graph.nodes, constraint)%>%slice(1:5)
```
The network constraint is 1 for all rebel groups suggesting high redundancy of connections, since most rebel groups only have one (or multiple) connections to a country, while countries have lower network constraint scores, since they have multiple connections with a larger number of rebel groups. 

```{r}
net<- as.network(conflict_subset, matrix.type = "edgelist", multiple = T)

tempo <-as.data.frame(brokerage(net, cl = get.vertex.attribute(net,"iel"))$z.nli)

head(brokerage(net, cl = get.vertex.attribute(net,"iel"))$z.nli)
```


