---
title: "Network Degree"
description: |
  A short description of the post.
author:
  - name: Abhijit Mahishi
    url: {}
date: 2022-05-11
output:
  distill::distill_article:
    self_contained: false
draft: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.

```{r}
graph.density(climate.ig)

graph.density(climate.ig, loops=TRUE)

igraph::degree(climate.ig)

igraph::degree(climate.ig,mode="in", loops = FALSE)
igraph::degree(climate.ig,mode="out", loops = FALSE)```

climate.nodes<-climate.nodes %>%
mutate(indegree=igraph::degree(climate.ig, mode="in",loops=FALSE),
outdegree=igraph::degree(climate.ig, mode="out",loops=FALSE))

hist(climate.nodes$indegree, main="Climate Influence: In-degree Distribution", xlab="Nominations Received")

hist(climate.nodes$outdegree, main="Climate Influence: Out-degree
Distribution ", xlab="Nominations made")
